COG-ED Manuscript

### 2021-12-16 06_Paper/COG-ED/Manuscript.Rmd
keep incorrect RTs
wrote results

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit

@@

    # replace the RTs of incorrect trials with NA for better handling

    pipelines_data[[i]]$rt[pipelines_data[[i]]$correct == 0] <- NA

@@

  # prepare table
  h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef), 
                                          m1_h2b.fixef[,c(1, 2, 5)]))
  h2b_result.table$ranef.sd <- NA
  h2b_result.table$ranef.sd[c(1,2)] <- m1_h2b.ranef$sdcor[c(1,2)]

@@

  row.names(h2b_result.table) <- NULL
  h2b_result.table$Parameter[1:8] <- c("Intercept", "N-Back Level", "NFC", "d'", "RT", "Correct", "Post-Correct", "Level x NFC")
  # FIXME: display control variables? Spelling lower/upper case

  h2b_result.table[2:5] <- lapply(h2b_result.table[2:5], as.numeric)

  h2b_result.table[c(2,3,5)] <- round(h2b_result.table[c(2,3,5)], digits = 2)
  h2b_result.table[4] <- round(h2b_result.table[4], digits = 3)

@@

  h2b_result.table$`Random Effects (SD)`[3:8] <- paste0("")

  library(kableExtra)
  #replication_table <-
    kbl(h2b_result.table,
    caption = "Effects of n-back load level on subjective value controlled 
    for task performance (d’ and reaction time), correct and postcorrect trials.",
    booktabs = T,                          # no vertical lines
    escape = F,                            # correctly print special characters)
    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
            escape = F,                    # correctly print special characters
            threeparttable = T)            # line breaks in the footnote
  #FIXME delete leading zero for p-values

@@

  library(interactions)
  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
                    cond.int = T,                                       # print conditional intercepts
                    johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals,
                                                                        # create plot, adjust false discovery rate

  # save Johnson-Neyman plot
  h2b_jnplot <- m1_h2b.ss$jnplot

  # create interaction plot
  h2b_ssa.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                                x.label = "n back level", y.label = "subjective value",
                                legend.main = "NFC", interval = T) + theme_apa()

  # prepare SSA results for reporting ------------------------------------------

  library(huxtable)
  h2b_ssa.table <- as_huxtable(m1_h2b.ss)
  h2b_ssa.table[1,] <- c("Value of NFC", "Slope of N-Back Level", "Conditional Intercept")
  h2b_ssa.table <- h2b_ssa.table[-2,]

  h2b_ssa.table[2:4,1] <- c("- 1 SD", "Mean", "+ 1 SD")

@@

The multilevel model `r replication_table`

statistically significant effect of n-back load level `r apa_print(m1_h2b)$full_result$level_cwc`
controlled for performance and correct and post-correct answers

`r apa_print(m1_h2b)$full_result$nfc_cgm`
`r round((icc_h2b*100), digits = 0)` % of the total variance in subjective values can be explained by differences between subjects ($ICC =$ `r round(icc_h2b, digits = 2)`).

simple slopes analysis `r h2b_ssa.table`, `r h2b_jnplot`,`r h2b_ssa.plot`
statistically significant influence of n-back load level on subjective value, but no moderating effect of NFC

>>>>

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # 
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable

@@

    # # replace the RTs of incorrect trials with NA for better handling
    # 
    # pipelines_data[[i]]$rt[pipelines_data[[i]]$correct == 0] <- NA

@@

  # prepare table
  h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef[-c(6,7),]), 
                                          m1_h2b.fixef[-c(6,7),c(1, 2, 5)]))
  h2b_result.table$ranef.sd <- NA
  h2b_result.table$ranef.sd[c(1,2)] <- m1_h2b.ranef$sdcor[c(1,2)]

@@

  row.names(h2b_result.table) <- NULL
  h2b_result.table$Parameter[1:6] <- c("Intercept", "N-Back Level", "NFC", "d'", "RT", "Level x NFC")

  h2b_result.table[2:5] <- lapply(h2b_result.table[2:5], as.numeric)
  h2b_result.table[c(2,3,5)] <- round(h2b_result.table[c(2,3,5)], digits = 2)
  h2b_result.table[4] <- round(h2b_result.table[4], digits = 3)

@@

  h2b_result.table$`Random Effects (SD)`[3:6] <- paste0("")

  replication_table <-
    kbl(h2b_result.table,
    caption = "Effects of n-back load level on subjective value controlled 
    for task performance (d’ and reaction time), correct and postcorrect trials.",
    booktabs = T,                          # no vertical lines
    escape = F,                            # correctly print special characters)
    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
            escape = F,                    # correctly print special characters
            threeparttable = T)            # line breaks in the footnote

@@

  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
                    cond.int = T,                       # print conditional intercepts
                    control.fdr = T)                    # adjust false discovery rate

  #create table
  h2b_ss.table <- as_huxtable(m1_h2b.ss)
  h2b_ss.table[1,] <- c("Value of NFC", "Slope of N-Back Level", "Conditional Intercept")
  h2b_ss.table <- h2b_ss.table[-2,]
  h2b_ss.table[2:4,1] <- c("- 1 SD", "Mean", "+ 1 SD")

  # calculate Johnson-Neyman intervals
  h2b_jn <- johnson_neyman(model = m1_h2b, pred = level.cwc, modx = nfc.cgm, control.fdr = T)
  h2b_jn.int <- h2b_jn$bounds

  # save plot
  h2b_jn.plot <- h2b_jn$plot

  # create interaction plot
  h2b_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                               plot.points = T, point.shape = T,
                               x.label = "n back level", y.label = "subjective value",
                               legend.main = "NFC", interval = T) + theme_apa()    
```

@@

N-back level is a reliable predictor of subjective value (`r apa_print(m1_h2b)$full_result$level_cwc`), even after controlling for declining task performance (signal detection d’ and reaction time) as well as correct and post-correct answers. 
The results of the multilevel model are detailed in Table X. 
`r replication_table`
`r round((icc_h2b*100), digits = 0)` % of the total variance in subjective values can be explained by differences between subjects ($ICC =$ `r round(icc_h2b, digits = 2)`).
However, NFC has no statistically significant effect on subjective value (`r apa_print(m1_h2b)$full_result$nfc_cgm`).
The simple slopes analysis revealed a significant slope of n-back level for three different expressions of NFC (Table X, Figure X).
`r h2b_ss.table`
`r h2b_ss.plot`
The Johnson-Neyman plot (Figure x) visualizes the significance of the slope of n-back level at different values of NFC. The Johnson-Neyman interval is [`r h2b_jn.int`]. Consequently, the slope of n-back level is not significant for individuals with very low NFC values.    
`r h2b_jn.plot`
